---
title: "Untitled"
author: "Hoang-Chau Luong"
date: "6/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
options(scipen = 20)

theme_set(theme_light())
```

# **Import data**

```{r}
front_end <- read_csv("data/Front-end dataset.csv") %>%
  mutate(date = as.POSIXct(timestamp/1e3, origin = "1970-01-01", tz = "UTC-7")) %>%
  select(-6, -7)

back_end <- read_csv("data/backend_dataset-2206.csv") %>%
  mutate(date = as.POSIXct(timestamp/1e3, origin = "1970-01-01", tz = "UTC-7"))
```

## **Join Table**

### **New user**

```{r}
new_user <- front_end %>%
  select(id, screenid) %>%
  unique() %>%
  filter(screenid != 11) %>%
  group_by(id) %>%
  summarise(type = "new") %>%
  ungroup()
```

### **Front end new user**

```{r}
front_end_ui <- front_end %>%
  left_join(new_user, by = "id") %>%
  mutate(type = ifelse(is.na(type), "old", type))
```

### **User type**

```{r}
user_type <- front_end_ui %>%
  group_by(id, type) %>%
  summarize(n = n()) %>%
  select(-n) %>%
  ungroup()
```


### **User have B**

```{r}
user_B <- back_end %>%
  filter(stepresult == "B") %>%
  select(id, stepresult) %>%
  unique()
```


### **Back end list id**

```{r}
back_end_list_id <- back_end %>%
  select(id) %>%
  unique()
```

#### **Number of B each user**

```{r}
B_status_backend <- back_end %>%
  filter(stepresult == "B") %>%
  group_by(id) %>%
  summarize(B_num = n()) %>%
  right_join(back_end_list_id, by = "id") %>%
  mutate(B_num = ifelse(is.na(B_num), 0, B_num))
```

### **User retry**

```{r}
user_retry <- back_end %>%
  mutate(encode = ifelse(stepresult == "B", 1, 0)) %>%
  group_by(id) %>%
  mutate(next_code = lead(encode, order_by = id)) %>%
  mutate(have_retrived = ((encode == 0 & next_code == 1) | 
                            (encode == 0 & next_code == 0))) %>%
  filter(have_retrived == TRUE) %>%
  select(id) %>%
  unique()
```


#### **Number of retry each user**

```{r}
number_user_retry <- back_end %>%
  mutate(encode = ifelse(stepresult == "B", 1, 0)) %>% 
  group_by(id) %>%
  arrange(date) %>% 
  mutate(next_code = lead(encode, order_by = id)) %>% 
  ungroup() %>%
  filter(!is.na(next_code)) %>%
  group_by(id) %>%
  summarize(retry_rate = sum(encode == 0 & next_code == 0) + sum(encode == 0 & next_code == 1)) %>%
  right_join(back_end_list_id) %>%
  mutate(retry_rate = ifelse(is.na(retry_rate), 0, retry_rate))
```

#### **Number of retry each user & B status**

```{r}
number_user_retry_and_B_status <- number_user_retry %>%
  left_join(B_status_backend, by = "id") %>%
  mutate(B_num = ifelse(B_num>=1, 1, 0))
```

#### **Number of retry each user & type user**

```{r}
number_user_retry_and_user_type <- number_user_retry %>%
  inner_join(user_type)
```

#### **Number of retry each user & type user & B status**
```{r}
number_user_retry_and_B_status_and_user_type <- number_user_retry_and_B_status %>%
  inner_join(user_type)
```


# **Analysis**

## **Retry Rate**

```{r}
back_end %>%
  inner_join(user_type, by = "id") %>%
  mutate(encode = ifelse(stepresult == "-FACJ", 0, 1)) %>% 
  arrange(id, date) %>% 
  group_by(id) %>% 
  mutate(next_code = lead(encode)) %>%
  ungroup() %>% 
  group_by(type, encode, next_code) %>%
  summarise( 
    n = n()
  ) %>%
  filter(encode == 0) %>%
  ungroup() %>%
  gt::gt()
```

## **Q3. What is the distribution of requests by the error for each UI? Does the new UI help reduce FACJ error?**

```{r}
back_end %>%
  filter(stepresult != "B") %>%
  inner_join(user_type, by = "id") %>%
  group_by(stepresult, type) %>%
  summarise(
    n = n()
  ) %>%
  ungroup() %>%
  ggplot(aes(x = fct_reorder(stepresult, n), y = n, fill = type)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  theme(plot.title = element_text(face = "bold", size = 20),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
#        axis.text.y = element_blank(),
#        axis.ticks.y = element_blank(),
        strip.background = element_rect(fill="#E0ED87"),
        strip.text = element_text(colour = 'black'),
        legend.position="right",
        legend.title = element_blank(),
        legend.text = element_text(face = "bold", size = 10)
      ) 
```

```{r}
question3_error_distribution  <- back_end %>%
  filter(stepresult != "B") %>%
  inner_join(user_type, by = "id") %>%
  group_by(stepresult, type) %>%
  summarise(
    n = n()
  ) %>%
  filter(stepresult == "-FACJ") %>%
  inner_join(
  back_end %>%
  filter(stepresult != "B") %>%
  inner_join(user_type, by = "id") %>%
  group_by(type) %>%
  summarise(
    total = n()
  ), by = "type")


write.csv(question3_error_distribution, "question3_error_distribution.csv")
```














