---
title: "Analysis On Bank A, B, C, D"
author: "Hoang-Chau Luong"
date: "6/22/2022"
output:
  html_document:
    number_sections: yes
    toc: yes
    code_folding: hide
    theme: readable
    highlight: haddock
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(highcharter)
library(gt)
library(ggthemes)
library(timetk)
library(tidyverse)
library(lubridate)
```

# **Import Data & Cleaning**

## **Bank A**

```{r warning=FALSE, message=FALSE}
bank_A <- read_csv("data/Bank_A.csv")

extract_day_month <- function(tibble){
  tibble %>%
    mutate(
    day = substr(Date, 1, 2),
    day = gsub("-", "", day),
    month = substr(Date, str_length(Date)-1, str_length(Date)),
    year = 2020,
    Date = as.Date(paste(year, month, day, sep="-"), "%Y-%m-%d")
  ) %>%
    select(-day, -month, -year)
}

bank_A <- bank_A %>%
  extract_day_month() 

bank_A <- bank_A %>%
  mutate(
    TheDangOTrangThaiKhongGiaoDichDuoc = gsub("-", "0", TheDangOTrangThaiKhongGiaoDichDuoc),
    SaiOTP = gsub("-", "0", SaiOTP),
    TheDaLienKet = gsub("-", "0", TheDaLienKet)
  ) %>%
  mutate(
    TheDangOTrangThaiKhongGiaoDichDuoc = as.numeric(TheDangOTrangThaiKhongGiaoDichDuoc),
    SaiOTP = as.numeric(SaiOTP),
    TheDaLienKet = as.numeric(TheDaLienKet)
  )

glimpse(bank_A)
```

## **Bank B**

```{r warning=FALSE, message=FALSE}
bank_B <- read_csv("data/Bank_B.csv")

bank_B <- bank_B %>%
  extract_day_month() 

bank_B <- bank_B %>%
  mutate(
    SaiThongTinKhachHang = gsub("-", "0", SaiThongTinKhachHang),
    TaiKhoanNganHangBiKhoa = gsub("-", "0", TaiKhoanNganHangBiKhoa),
    HeThongDangCoLoi = gsub("-", "0", HeThongDangCoLoi),
    TheKhongHoTro = gsub("-", "0", TheKhongHoTro),
    OTPHetHan = gsub("-", "0", OTPHetHan),
    TheDaLienKet = gsub("-", "0", TheDaLienKet),
  ) %>%
  mutate(
    SaiThongTinKhachHang = as.numeric(SaiThongTinKhachHang),
    TaiKhoanNganHangBiKhoa =as.numeric(TaiKhoanNganHangBiKhoa),
    HeThongDangCoLoi = as.numeric(HeThongDangCoLoi),
    TheKhongHoTro = as.numeric(TheKhongHoTro),
    OTPHetHan = as.numeric(OTPHetHan),
    TheDaLienKet = as.numeric(TheDaLienKet),
  )

glimpse(bank_B)
```

## **Bank C**

```{r warning=FALSE, message=FALSE}
bank_C <- read_csv("data/Bank_C.csv")

bank_C <- bank_C %>%
  extract_day_month() 

bank_C <- bank_C %>%
  mutate(
    GiaoDichDangXuLy = gsub("-", "0", GiaoDichDangXuLy),
    ThongTinXacThucKhongHopLe = gsub("-", "0", ThongTinXacThucKhongHopLe),
  ) %>%
  mutate(
    KhongNhanDuocPhanHoiTuNganHang = as.numeric(KhongNhanDuocPhanHoiTuNganHang),
    GiaoDichDangXuLy = as.numeric(GiaoDichDangXuLy),
    ThongTinXacThucKhongHopLe =as.numeric(ThongTinXacThucKhongHopLe),
  )

glimpse(bank_C)
```

## **Bank D**

```{r warning=FALSE, message=FALSE}
bank_D <- read_csv("data/Bank_D.csv")

bank_D <- bank_D %>%
  extract_day_month() 

bank_D <- bank_D %>%
  mutate(
    KhachHangHuyGiaoDich = gsub("-", "0", KhachHangHuyGiaoDich),
    ThongTinDangNhapKhongDung = gsub("-", "0", ThongTinDangNhapKhongDung),
    HeThongNganHangDangCoLoi = gsub("-", "0", HeThongNganHangDangCoLoi),
    TheDaLienKet = gsub("-", "0", TheDaLienKet),
    HeThongNganHangDangCoLoi2 = gsub("-", "0", HeThongNganHangDangCoLoi2),
    OTPHetHan = gsub("-", "0", OTPHetHan),
  ) %>%
  mutate(
    KhachHangHuyGiaoDich = as.numeric(KhachHangHuyGiaoDich),
    ThongTinDangNhapKhongDung =as.numeric(ThongTinDangNhapKhongDung),
    HeThongNganHangDangCoLoi = as.numeric(HeThongNganHangDangCoLoi),
    TheDaLienKet = as.numeric(TheDaLienKet),
    HeThongNganHangDangCoLoi2 = as.numeric(HeThongNganHangDangCoLoi2),
    OTPHetHan = as.numeric(OTPHetHan),
  )

glimpse(bank_D)
```


# **Time series analysiss - Exploring Seasonality and Pattern**

## **Bank A**
```{r warning=FALSE, message=FALSE}
# cols_low_value <- c("SaiOTP", "TheDaLienKet", "TheDangOTrangThaiKhongGiaoDichDuoc")

time_series_bank_A <- bank_A %>%
  pivot_longer(!Date, names_to = "name", values_to = "value")
```

## **Bank B**

```{r warning=FALSE, message=FALSE}
time_series_bank_B <- bank_B %>%
  pivot_longer(!Date, names_to = "name", values_to = "value")
```

## **Bank C**

```{r warning=FALSE, message=FALSE}
time_series_bank_C <- bank_C %>%
  pivot_longer(!Date, names_to = "name", values_to = "value")
```

## **Bank D**

```{r warning=FALSE, message=FALSE}
time_series_bank_D <- bank_D %>%
  pivot_longer(!Date, names_to = "name", values_to = "value")
```


```{r warning=FALSE, message=FALSE}
convert_date_ts <- function(data, unit = "day"){
  
  new_data <- data %>% 
    mutate(Date = floor_date(Date, unit = unit))
  
  return(new_data)
}
```

## **Daily**

### **Bank A**
```{r warning=FALSE, message=FALSE}
time_series_bank_A %>%
  convert_date_ts() %>%
  group_by(name) %>%
  plot_time_series(
    .date_var = Date,
    .value = value,
    .facet_ncol = 2,
    .smooth_color = "#18BC9C",
    .smooth_size = 0.5
  )
```

### **Bank B**

```{r warning=FALSE, message=FALSE}
time_series_bank_B %>%
  convert_date_ts() %>%
  group_by(name) %>%
  plot_time_series(
    .date_var = Date,
    .value = value,
    .facet_ncol = 2,
    .smooth_color = "#18BC9C",
    .smooth_size = 0.5
  )
```

### **Bank C**

```{r warning=FALSE, message=FALSE}
time_series_bank_C %>%
  convert_date_ts() %>%
  group_by(name) %>%
  plot_time_series(
    .date_var = Date,
    .value = value,
    .facet_ncol = 2,
    .smooth_color = "#18BC9C",
    .smooth_size = 0.5
  )
```

### **Bank D**

```{r warning=FALSE, message=FALSE}
time_series_bank_D %>%
  convert_date_ts() %>%
  group_by(name) %>%
  plot_time_series(
    .date_var = Date,
    .value = value,
    .facet_ncol = 2,
    .smooth_color = "#18BC9C",
    .smooth_size = 0.5
  )
```

## **Weekly**

```{r warning=FALSE, message=FALSE}
time_series_bank_A %>%
  convert_date_ts(unit = "week") %>%
  group_by(name) %>%
  plot_time_series(
    .date_var = Date,
    .value = value,
    .facet_ncol = 2,
    .smooth_color = "#18BC9C",
    .smooth_size = 0.5
  )
```

## **Monthly**

```{r warning=FALSE, message=FALSE}
time_series_bank_A %>%
  convert_date_ts(unit = "month") %>%
  group_by(name) %>%
  plot_time_series(
    .date_var = Date,
    .value = value,
    .facet_ncol = 2,
    .smooth_color = "#18BC9C",
    .smooth_size = 0.5
  )
```

## **Outlier Detection**

```{r warning=FALSE, message=FALSE}
time_series_bank_A %>%
 group_by(name) %>%
  plot_anomaly_diagnostics(
    .date = Date,
    .value = value,
    .facet_ncol = 2,
    .interactive=FALSE,
    .title = "Anomaly Diagnostics Dow Jones",
    .anom_color ="#FB3029", 
    .max_anomalies = 0.07, 
    .alpha = 0.05
    )
```

## **Seasonality Patterns**

```{r warning=FALSE, message=FALSE}
# time_series_bank_A %>% 
#   plot_seasonal_diagnostics(
#     .date_var = Date,
#     .value = value,
#     .interactive = FALSE,
#     .geom_color = "#4E79A7"
#   )
```



# **Analysis**

## **Time series plot**

```{r warning=FALSE, message=FALSE}
bank_A_April_plot <- time_series_bank_A %>%
  filter(month(Date) == 4) %>%
  ggplot(aes(Date, value)) +
  geom_line() +
  facet_wrap(~ name, scales = "free") +
  geom_smooth(method = "lm")
  

bank_A_May_plot <- time_series_bank_A %>%
  filter(month(Date) == 5) %>%
  ggplot(aes(Date, value)) +
  geom_line() +
  facet_wrap(~ name, scales = "free") +
  geom_smooth(method = "lm")


time_series_bank_A %>%
  ggplot(aes(Date, value)) +
  geom_line(aes(group = name, col = name), size = 1) 

sbank_A_April_plot
bank_A_May_plot
```

## **GiaoDichThanhCong vs ThatBai**

### **Bank A**

```{r warning=FALSE, message=FALSE}
number_of_failures_bank_A <- bank_A %>%
  select(-GiaoDichThanhCong) %>%
  pivot_longer(!Date, names_to = "name", values_to = "value") %>%
  group_by(Date) %>%
  summarise(
    ThatBai = sum(value, na.rm = TRUE)
  )

bank_A %>% 
  inner_join(number_of_failures, by = "Date") %>%
  group_by(Date) %>%
  summarise(success_rate = GiaoDichThanhCong/(GiaoDichThanhCong+ThatBai)) %>%
  ggplot(aes(Date, success_rate)) +
  geom_line() +
  geom_smooth(method = "lm")
```

### **Bank B**

```{r warning=FALSE, message=FALSE}
number_of_failures_bank_B <- bank_B %>%
  select(-GiaoDichThanhCong) %>%
  pivot_longer(!Date, names_to = "name", values_to = "value") %>%
  group_by(Date) %>%
  summarise(
    ThatBai = sum(value, na.rm = TRUE)
  )

bank_B %>% 
  inner_join(number_of_failures, by = "Date") %>%
  group_by(Date) %>%
  summarise(success_rate = GiaoDichThanhCong/(GiaoDichThanhCong+ThatBai)) %>%
  ggplot(aes(Date, success_rate)) +
  geom_line() +
  geom_smooth(method = "lm")
```

### **Bank C**

```{r warning=FALSE, message=FALSE}
number_of_failures_bank_C <- bank_C %>%
  select(-GiaoDichThanhCong) %>%
  pivot_longer(!Date, names_to = "name", values_to = "value") %>%
  group_by(Date) %>%
  summarise(
    ThatBai = sum(value, na.rm = TRUE)
  )

bank_C %>% 
  inner_join(number_of_failures, by = "Date") %>%
  group_by(Date) %>%
  summarise(success_rate = GiaoDichThanhCong/(GiaoDichThanhCong+ThatBai)) %>%
  ggplot(aes(Date, success_rate)) +
  geom_line() +
  geom_smooth(method = "lm")
```

### **Bank D**

```{r warning=FALSE, message=FALSE}
number_of_failures_bank_D <- bank_D %>%
  select(-GiaoDichThanhCong) %>%
  pivot_longer(!Date, names_to = "name", values_to = "value") %>%
  group_by(Date) %>%
  summarise(
    ThatBai = sum(value, na.rm = TRUE)
  )

bank_D %>% 
  inner_join(number_of_failures, by = "Date") %>%
  group_by(Date) %>%
  summarise(success_rate = GiaoDichThanhCong/(GiaoDichThanhCong+ThatBai)) %>%
  ggplot(aes(Date, success_rate)) +
  geom_line() +
  geom_smooth(method = "lm")
```


## **Compare with lag day**

```{r warning=FALSE, message=FALSE}
lag_bank_A <- bank_A %>%
  mutate(
    lag_TheChuaBatEcom = lag(TheChuaBatEcom),
    lag_GiaoDichThanhCong = lag(GiaoDichThanhCong),
    lag_SaiSoDienThoai = lag(SaiSoDienThoai),
    lag_SaiTenChuThe = lag(SaiTenChuThe),
    lag_SaiSoCMND = lag(SaiSoCMND),
    lag_SaiNgayPhatHanhThe = lag(SaiNgayPhatHanhThe),
    lag_KhongNhanDuocXacThucOTP = lag(KhongNhanDuocXacThucOTP),
    lag_TheDangOTrangThaiKhongGiaoDichDuoc = lag(TheDangOTrangThaiKhongGiaoDichDuoc),
    lag_SaiOTP = lag(SaiOTP),
    lag_TheDaLienKet = lag(TheDaLienKet)
  )
```

```{r warning=FALSE, message=FALSE}
delta_bank_A <- bank_A %>%
  mutate(
    delta_TheChuaBatEcom = TheChuaBatEcom - lag(TheChuaBatEcom),
    delta_GiaoDichThanhCong = GiaoDichThanhCong - lag(GiaoDichThanhCong),
    delta_SaiSoDienThoai = SaiSoDienThoai - lag(SaiSoDienThoai),
    delta_SaiTenChuThe = SaiTenChuThe - lag(SaiTenChuThe),
    delta_SaiSoCMND = SaiSoCMND - lag(SaiSoCMND),
    delta_SaiNgayPhatHanhThe = SaiNgayPhatHanhThe - lag(SaiNgayPhatHanhThe),
    delta_KhongNhanDuocXacThucOTP = KhongNhanDuocXacThucOTP - lag(KhongNhanDuocXacThucOTP),
    delta_TheDangOTrangThaiKhongGiaoDichDuoc = TheDangOTrangThaiKhongGiaoDichDuoc- lag(TheDangOTrangThaiKhongGiaoDichDuoc),
    delta_SaiOTP = SaiOTP - lag(SaiOTP),
    delta_TheDaLienKet = SaiOTP - lag(TheDaLienKet)
  )

delta_bank_A %>%
  select(Date, starts_with("delta")) %>%
  filter()
```



# **Hypothesis Testing**

## **Success Rate of May higher than April**

### **Bank A**

```{r warning=FALSE, message=FALSE}
bank_A %>%
  inner_join(number_of_failures, by = "Date") %>%
  mutate(month = month(Date)) %>%
  group_by(month) %>%
  summarise( 
    total_success = sum(GiaoDichThanhCong),
    total_failure = sum(ThatBai),
    success_rate = total_success/(total_success+total_failure)
    )

z_test_hypothesis <- function(s1, s2, f1, f2){
  p_total <- (s1+s2)/(s1+f1+s2+f2)
  p1_hat <- s1/(s1+f1)
  p2_hat <- s2/(s2+f2)
  
  p_hat <- ((s1+f1)*p1_hat + (s2+f2)*p2_hat)/(s1+f1+s2+f2)
  
  z_obs <- (p1_hat-p2_hat)/sqrt(p_hat*(1-p_hat)*(1/(s1+f1) + 1/(s1+f1))) 
  
  p_value <- 1-pnorm(abs(z_obs))
  
  return(c(p_total, p1_hat, p2_hat, p_value))
}

z_test_hypothesis(8401, 9322, 22279, 20945)
```


### **Bank B**

```{r warning=FALSE, message=FALSE}
bank_B %>%
  inner_join(number_of_failures_bank_B, by = "Date") %>%
  mutate(month = month(Date)) %>%
  group_by(month) %>%
  summarise( 
    total_success = sum(GiaoDichThanhCong),
    total_failure = sum(ThatBai),
    success_rate = total_success/(total_success+total_failure)
    )

z_test_hypothesis(7020, 7236, 7125, 6385)
```

### **Bank C**

```{r warning=FALSE, message=FALSE}
bank_C %>%
  inner_join(number_of_failures_bank_C, by = "Date") %>%
  mutate(month = month(Date)) %>%
  group_by(month) %>%
  summarise( 
    total_success = sum(GiaoDichThanhCong),
    total_failure = sum(ThatBai),
    success_rate = total_success/(total_success+total_failure)
    )

z_test_hypothesis(11229, 9268, 30458, 27753)
```

### **Bank D**

```{r}
bank_D %>%
  inner_join(number_of_failures_bank_D, by = "Date") %>%
  mutate(month = month(Date)) %>%
  group_by(month) %>%
  summarise( 
    total_success = sum(GiaoDichThanhCong),
    total_failure = sum(ThatBai),
    success_rate = total_success/(total_success+total_failure)
    )

z_test_hypothesis(3607, 4952, 20921, 19088)
```

## **Which highest Error of each Bank**

```{r}
bank_A %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) 

bank_B %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) 

bank_C %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) 

bank_D %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) 

bank_A %>%
  pivot_longer(!Date, names_to = "name", values_to = "value") %>%
  select(name) %>%
  unique() %>%
  inner_join(bank_B %>%
            pivot_longer(!Date, names_to = "name", values_to = "value") %>%
            select(name) %>%
            unique(), by = "name")

bank_C %>%
  pivot_longer(!Date, names_to = "name", values_to = "value") %>%
  select(name) %>%
  unique() %>%
  inner_join(bank_B %>%
            pivot_longer(!Date, names_to = "name", values_to = "value") %>%
            select(name) %>%
            unique(), by = "name")

```

# **User type E, F, G**
```{r}
user_type <- read_csv("data/user_type.csv")
user_type <- user_type %>%
  mutate(
    type = rep(c("Android", "IOS"), 15),
    month = rep(c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5), 3)
  )

user_type %>%
  ggplot(aes(month, value, fill = type)) +
  geom_col() +
  facet_wrap(~Bank, scale = "free")
```

```{r}
bank_E <- read_excel('data/bank_efg.xlsx', sheet = 2)

bank_E %>%
  pivot_longer(!error, names_to = "name", values_to = "value") %>% 
  mutate(
    month = substr(name, str_length(name), str_length(name)),
    name = substr(name, 0, str_length(name)-2)
  ) %>%
  ggplot(aes(x = month, y = value, col = error, group = error)) +
  geom_line()
```

```{r}
time_series_bank_A %>%
  count(name, wt = value)

time_series_bank_B %>%
  count(name, wt = value)

time_series_bank_C %>%
  count(name, wt = value, sort = TRUE)

time_series_bank_D %>%
  count(name, wt = value, sort = TRUE)
```





