---
title: "Untitled"
author: "Hoang-Chau Luong"
date: "6/21/2022"
output: html_document
---

```{r}
Wine = read_excel('../input/australian-wines/AustralianWines2.xls', sheet = 1)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytuesdayR)
library(gt)
library(rmarkdown)
library(patchwork)
library(ggtext)

library(dunnr)
extrafont::loadfonts(device = "win", quiet = TRUE)
theme_set(theme_td())
set_geom_fonts()
# A coffee themed palette I found here: https://colorpalettes.net/color-palette-4281/
coffee_pal <- c("#a0583c", "#c08267", "#ccb9b1", "#616063", "#212123")
options(ggplot2.discrete.color = coffee_pal,
        ggplot2.discrete.fill = coffee_pal)
```

```{r}
tt <- tidytuesdayR::tt_load("2020-07-07")

coffee <- tt$coffee_ratings
```

|variable              |class     |description |
|:---------------------|:---------|:-----------|
|total_cup_points      |double    | Total rating/points (0 - 100 scale) |
|species               |character | Species of coffee bean (arabica or robusta) |
|owner                 |character | Owner of the farm |
|country_of_origin     |character | Where the bean came from |
|farm_name             |character | Name of the farm |
|lot_number            |character | Lot number of the beans tested |
|mill                  |character | Mill where the beans were processed |
|ico_number            |character | International Coffee Organization number |
|company               |character | Company name |
|altitude              |character | Altitude - this is a messy column - I've left it for some cleaning  |
|region                |character | Region where bean came from |
|producer              |character | Producer of the roasted bean |
|number_of_bags        |double    | Number of bags tested |
|bag_weight            |character | Bag weight tested |
|in_country_partner    |character | Partner for the country |
|harvest_year          |character | When the beans were harvested (year) |
|grading_date          |character | When the beans were graded|
|owner_1               |character | Who owns the beans|
|variety               |character | Variety of the beans |
|processing_method     |character | Method for processing|
|aroma                 |double    | Aroma grade |
|flavor                |double    | Flavor grade |
|aftertaste            |double    | Aftertaste grade |
|acidity               |double    | Acidity grade |
|body                  |double    | Body grade |
|balance               |double    | Balance grade |
|uniformity            |double    | Uniformity grade |
|clean_cup             |double    | Clean cup grade |
|sweetness             |double    | Sweetness grade |
|cupper_points         |double    | Cupper Points|
|moisture              |double    | Moisture Grade|
|category_one_defects  |double    | Category one defects (count) |
|quakers               |double    | quakers|
|color                 |character | Color of bean |
|category_two_defects  |double    |Category two defects (count)  |
|expiration            |character | Expiration date of the beans |
|certification_body    |character | Who certified it |
|certification_address |character | Certification body address |
|certification_contact |character | Certification contact |
|unit_of_measurement   |character | Unit of measurement |
|altitude_low_meters   |double    | Altitude low meters|
|altitude_high_meters  |double    | Altitude high meters |
|altitude_mean_meters  |double    | Altitude mean meters |

```{r}
skimr::skim(coffee)
```

```{r}
p <- coffee %>%
  ggplot(aes(x = total_cup_points)) +
  geom_boxplot(y = 0, fill = coffee_pal[1], outlier.shape = NA) +
  geom_jitter(aes(y = 1), color = coffee_pal[2],
              alpha = 0.3, height = 0.3, width = 0) +
  remove_axis("y")

p

coffee %>%
  filter(total_cup_points == min(total_cup_points)) %>%
  glimpse()

coffee <- coffee %>% filter(total_cup_points > 0)
p %+% coffee
```

```{r}
coffee %>%
  select(aroma:moisture) %>%
  pivot_longer(cols = everything()) %>%
  ggplot(aes(x = value)) +
  geom_boxplot(y = 0, fill = coffee_pal[1], outlier.shape = NA) +
  geom_jitter(aes(y = 1), color = coffee_pal[2],
              alpha = 0.3, height = 0.3, width = 0) +
  remove_axis("y") +
  facet_wrap(~name, ncol = 3)
```

```{r}
coffee %>%
  ggplot(aes(x = moisture)) +
  geom_boxplot(y = 0, fill = coffee_pal[1], outlier.shape = NA) +
  geom_jitter(aes(y = 1), color = coffee_pal[2],
              alpha = 0.3, height = 0.3, width = 0) +
  remove_axis("y")
```

```{r}
coffee %>%
  rowwise() %>%
  transmute(
    total_cup_points,
    sum_gradings = sum(c_across(aroma:cupper_points))
  ) %>%
  ggplot(aes(x = total_cup_points, y = sum_gradings)) +
  geom_point(color = coffee_pal[1], size = 2) +
  geom_abline(size = 1)
```

```{r}
coffee %>%
  select(aroma:cupper_points) %>%
  corrr::correlate(method = "pearson", use = "everything") %>%
  corrr::rplot() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.7))
```

```{r}
coffee %>%
  select(uniformity, clean_cup, sweetness) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  mutate(
    name = glue::glue(
      "{name} ({scales::percent(mean(value == 10))} values = 10.0)"
    )
  ) %>%
  ggplot(aes(x = value, y = 1)) +
  geom_jitter(alpha = 0.3, width = 0, color = coffee_pal[3]) +
  facet_wrap(~name, ncol = 1) +
  remove_axis("y") +
  scale_x_continuous(breaks = 0:10)
```

```{r}
coffee %>% count(species)

coffee %>%
  count(country_of_origin, sort = TRUE) %>%
  mutate(
    country_of_origin = country_of_origin %>%
      fct_explicit_na() %>%
      fct_reorder(n)
  ) %>%
  ggplot(aes(y = country_of_origin, x = n)) +
  geom_col(fill = coffee_pal[1]) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(y = NULL)
```

```{r}
coffee %>%
  mutate(
    country_of_origin  = country_of_origin %>%
      fct_explicit_na() %>%
      fct_lump(n = 10) %>%
      fct_reorder(total_cup_points)
  ) %>%
  ggplot(aes(y = country_of_origin, x = total_cup_points)) +
  geom_boxplot(fill = coffee_pal[3]) +
  labs(y = NULL)
```

```{r}
coffee %>%
  mutate(
    variety = variety %>%
      fct_explicit_na() %>%
      fct_lump_min(10, other_level = "Other (n<10)")
  ) %>%
  count(variety) %>%
  mutate(variety = fct_reorder(variety, n)) %>%
  ggplot(aes(y = variety, x = n)) +
  geom_col(fill = coffee_pal[2]) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(y = NULL)
```

```{r}
coffee <- coffee %>%
  mutate(variety = ifelse(variety == "Other", NA_character_, variety))
```


```{r}
d <- coffee %>%
  mutate(
    in_country_partner = fct_lump(in_country_partner, 10)
  ) %>%
  add_count(in_country_partner) %>%
  mutate(in_country_partner = fct_reorder(in_country_partner, n))
p1 <- d %>%
  distinct(in_country_partner, n) %>%
  ggplot(aes(y = in_country_partner, x = n)) +
  geom_col(fill = coffee_pal[1]) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(y = NULL)
p2 <- d %>%
  ggplot(aes(y = in_country_partner, x = total_cup_points)) +
  geom_boxplot(fill = coffee_pal[2]) +
  labs(y = NULL) +
  theme(axis.text.y = element_blank())
p1 | p2
```

```{r}
d <- coffee %>%
  add_count(color) %>%
  mutate(color = fct_reorder(color, n))
p1 <- d %>%
  distinct(color, n) %>%
  ggplot(aes(y = color, x = n)) +
  geom_col(fill = coffee_pal[1]) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(y = NULL)
p2 <- d %>%
  ggplot(aes(y = color, x = total_cup_points)) +
  geom_boxplot(fill = coffee_pal[2]) +
  labs(y = NULL) +
  theme(axis.text.y = element_blank())
p1 | p2
```


```{r}
d %>%
  count(harvest_year, sort = T) %>%
  paged_table()
```

```{r}
coffee <- coffee %>%
  mutate(
    harvest_year_num = harvest_year %>%
      str_extract("\\d{4}") %>%
      as.numeric()
  )
coffee %>%
  count(harvest_year, harvest_year_num, sort = T) %>%
  paged_table()
```

```{r}
d <- coffee %>%
  add_count(processing_method) %>%
  mutate(processing_method = fct_reorder(processing_method, n))
p1 <- d %>%
  distinct(processing_method, n) %>%
  ggplot(aes(y = processing_method, x = n)) +
  geom_col(fill = coffee_pal[1]) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(y = NULL)
p2 <- d %>%
  ggplot(aes(y = processing_method, x = total_cup_points)) +
  geom_boxplot(fill = coffee_pal[2]) +
  labs(y = NULL) +
  theme(axis.text.y = element_blank())
p1 | p2
```

```{r}
coffee <- coffee %>%
  mutate(
    # Convert both to date objects
    expiration = lubridate::mdy(expiration),
    grading_date = lubridate::mdy(grading_date)
  )
coffee %>%
  mutate(
    days_from_expiration = expiration - grading_date
  ) %>%
  count(days_from_expiration)
```

```{r}
d <- coffee %>%
  mutate(
    across(
      c(category_one_defects, category_two_defects, quakers),
      # Group counts above 5 together
      ~cut(., breaks = c(0:5, 100), include.lowest = TRUE, right = FALSE,
           labels = c(0:4, "5+"))
    )
  ) %>%
  select(where(is.factor), total_cup_points) %>%
  pivot_longer(cols = -total_cup_points,
               names_to = "defect", values_to = "n_defects") %>%
  filter(!is.na(n_defects))

p1 <- d %>%
  filter(defect == "category_one_defects") %>%
  ggplot(aes(y = n_defects)) +
  geom_bar(fill = coffee_pal[1]) +
  scale_x_continuous(NULL, expand = expansion(c(0, 0.05)))
p2 <- d %>% 
  filter(defect == "category_one_defects") %>%
  ggplot(aes(y = n_defects, x = total_cup_points)) +
  geom_boxplot(fill = coffee_pal[3]) +
  labs(x = NULL, y = NULL)


(
  (p1 + labs(y = "Category 1") | p2)
) /
  (
    (p1 %+% filter(d, defect == "category_two_defects") +
       labs(y = "Category 2") |
       p2 %+% filter(d, defect == "category_two_defects"))
  ) /
  (
    (p1 %+% filter(d, defect == "quakers") +
       labs(y = "Quakers", x = "Count") |
       (p2 %+% filter(d, defect == "quakers") +
          labs(x = "Total cup points")))
  )
```

```{r}
coffee %>%
  count(
    altitude, altitude_mean_meters, altitude_low_meters, altitude_high_meters,
    unit_of_measurement, sort = T
  ) %>%
  paged_table()

coffee %>%
  filter(unit_of_measurement == "ft", !is.na(altitude)) %>%
  #filter(altitude == "4300") %>%
  count(altitude, unit_of_measurement, altitude_mean_meters, sort = T) %>%
  # Re-calculate the altitude in feet to see if it matches
  mutate(feet_manual = altitude_mean_meters * 3.28) %>%
  paged_table()

coffee %>%
  filter(!is.na(altitude_mean_meters)) %>%
  ggplot(aes(x = altitude_mean_meters)) +
  geom_boxplot(y = 0, fill = coffee_pal[2]) +
  scale_x_log10() +
  remove_axis("y")

coffee %>%
  select(country_of_origin, altitude, unit_of_measurement,
         altitude_mean_meters) %>%
  arrange(desc(altitude_mean_meters)) %>%
  filter(altitude_mean_meters > 2000) %>%
  gt()

coffee %>%
  filter(str_detect(altitude, regex("sea", ignore_case = T))) %>%
  select(matches("altitu")) %>%
  gt()

coffee %>%
  select(country_of_origin, altitude, unit_of_measurement,
         altitude_mean_meters, producer, country_of_origin) %>%
  arrange(desc(altitude_mean_meters)) %>%
  filter(altitude_mean_meters <= 10) %>%
  gt()

coffee <- coffee %>%
  mutate(
    altitude_mean_meters_fixed = case_when(
      altitude == "1800 meters (5900" ~ 1800,
      altitude_mean_meters == 190164 ~ 1901,
      altitude_mean_meters == 110000 ~ 1100,
      str_detect(altitude, "^meters above") ~ altitude_mean_meters / 1000.0,
      # Assume anything above 3000 needs to be converted from feet
      altitude_mean_meters > 3000 ~ 0.3048 * altitude_mean_meters,
      TRUE ~ altitude_mean_meters
    )
  )
coffee %>%
  filter(!is.na(altitude_mean_meters_fixed)) %>%
  ggplot(aes(x = altitude_mean_meters_fixed)) +
  geom_boxplot(y = 0, fill = coffee_pal[2]) +
  remove_axis("y")

coffee %>%
  select(aroma:cupper_points, altitude_mean_meters_fixed) %>%
  filter(!is.na(altitude_mean_meters_fixed)) %>%
  pivot_longer(cols = -altitude_mean_meters_fixed,
               names_to = "grading", values_to = "score") %>%
  ggplot(aes(x = altitude_mean_meters_fixed, y = score)) +
  geom_point(alpha = 0.3, color = coffee_pal[2]) +
  geom_smooth(method = "loess", formula = "y ~ x", color = coffee_pal[3]) +
  facet_wrap(~grading, ncol = 2, scales = "free_y") +
  scale_y_continuous(breaks = seq(0, 10, 2))

coffee %>%
  filter(!is.na(altitude_mean_meters_fixed)) %>%
  ggplot(aes(x = altitude_mean_meters_fixed, y = total_cup_points)) +
  geom_point(alpha = 0.3, color = coffee_pal[2]) +
  geom_smooth(method = "loess", formula = "y ~ x", color = coffee_pal[3]) +
  scale_y_continuous(breaks = seq(0, 100, 10))
```

```{r}
set.seed(74)
sample(
  c("aroma", "flavor", "aftertaste", "acidity", "body",
    "balance", "cupper_points"),
  size = 1
)
```

```{r}
# Some minor pre-processing
coffee <- coffee %>%
  mutate(
    variety = fct_explicit_na(variety),
    across(where(is.character), factor)
  )

library(tidymodels)
set.seed(42)
coffee_split <- initial_split(coffee, prop = 3/4, strata = flavor)
coffee_train <- training(coffee_split)
coffee_test <- testing(coffee_split)

coffee_resamples <- vfold_cv(coffee_train, v = 5, strata = flavor)
```

```{r}
coffee_rec <-
  recipe(
    flavor ~
      species + country_of_origin + processing_method + color +
      in_country_partner + variety + aroma + aftertaste + acidity + body +
      balance + uniformity + clean_cup + sweetness + cupper_points + moisture +
      category_one_defects + category_two_defects + quakers +
      altitude_mean_meters_fixed,
    data = coffee_train
  ) %>%
  # Where missing, impute categorical variables with the most common value
  step_impute_mode(all_nominal_predictors()) %>%
  # Some of these categorical variables have too many levels, group levels
  #  with <5% frequency 
  step_other(country_of_origin, variety, in_country_partner, processing_method,
             threshold = 0.05) %>%
  # These two numerical predictors have some missing value, so impute with mean
  step_impute_mean(quakers, altitude_mean_meters_fixed) %>%
  # Normalize (0 mean, 1 SD) all numerical predictors
  step_normalize(all_numeric_predictors()) %>%
  # Use splines in the altitude variable to capture it's non-linearity.
  step_ns(altitude_mean_meters_fixed, deg_free = 4) %>%
  # Finally, create the dummy variables (note that this step must come *after*
  #  normalizing numerical variables)
  step_dummy(all_nominal_predictors())
coffee_rec

coffee_baked <- bake(prep(coffee_rec), new_data = NULL)
coffee_baked %>% paged_table()
```

```{r}
# Speed up the tuning with parallel processing
n_cores <- parallel::detectCores(logical = FALSE)
library(doParallel)
cl <- makePSOCKcluster(n_cores - 1)
registerDoParallel(cl)
```

```{r}
lm_spec <- linear_reg() %>%
  set_engine("lm")
lm_workflow <- workflow() %>%
  add_recipe(coffee_rec) %>%
  add_model(lm_spec)
lm_fit_train <- lm_workflow %>%
  fit(data = coffee_train)
lm_fit <- last_fit(lm_fit_train, coffee_split)

collect_metrics(lm_fit)

collect_predictions(lm_fit) %>%
  ggplot(aes(x = flavor, y = .pred)) +
  geom_point(color = coffee_pal[1], alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, size = 1.5)
```

```{r}
lasso_spec <- linear_reg(penalty = tune(), mixture = 1) %>%
  set_engine("glmnet")

# Define the lambda values to try when tuning
lasso_lambda_grid <- grid_regular(penalty(), levels = 50)

lasso_workflow <- workflow() %>%
  add_recipe(coffee_rec) %>%
  add_model(lasso_spec)

library(tictoc) # A convenient package for timing
tic()
lasso_tune <-
  tune_grid(
    lasso_workflow,
    resamples = coffee_resamples,
    grid = lasso_lambda_grid
  )
toc()

show_best(lasso_tune, metric = "rmse")
```

```{r}
collect_metrics(lasso_tune) %>%
  #filter(!is.na(std_err)) %>%
  ggplot(aes(x = penalty, y = mean)) +
  geom_line(size = 1, color = coffee_pal[1]) +
  geom_point(color = coffee_pal[1]) +
  geom_ribbon(aes(ymin = mean - std_err, ymax = mean + std_err),
              alpha = 0.5, fill = coffee_pal[3]) +
  facet_wrap(~.metric, ncol = 1, scales = "free_y") +
  scale_x_log10()
```

```{r}
lasso_best_workflow <- lasso_workflow %>%
  finalize_workflow(select_best(lasso_tune, metric = "rmse"))
lasso_fit <- last_fit(lasso_best_workflow, coffee_split)

collect_metrics(lasso_fit)

library(vip)
lasso_fit %>%
  extract_fit_engine() %>%
  vi(
    # This step seems to be necessary for glmnet objects
    lambda =  select_best(lasso_tune, metric = "rmse")$penalty
  ) %>%
  mutate(Variable = fct_reorder(Variable, Importance)) %>%
  ggplot(aes(x = Importance, y = Variable, fill = Sign)) +
  geom_col() +
  scale_x_continuous(expand = c(0, 0)) +
  labs(y = NULL) +
  theme(legend.position = c(0.3, 0.3))
```



